Bootstrap Learning via Modular Concept Discovery

### 2013-04-23 drafts/ijcai2013/camera_ready/Dechter.IJCAI13.CameraReady.tex
Reformatted titles to mixed case.

\title{Bootstrap learning via modular concept discovery}

@@

\section{Extracting concepts from programs}

@@

\subsection{Representing typed functional programs as binary trees}

@@

\subsection{A stochastic grammar over programs}
\label{sec:stochgrammar}

@@

\subsection{Best-first enumeration of programs}
In order to explore the frontier of most promising programs, we need a
procedure that enumerates the $N$ most probable expressions. There has
been recent interest in this problem, most of it focused on
enumerating the shortest program satisfying some
criterion~\cite{DBLP:conf/sfp/Katayama05,DBLP:conf/aaip/YakushevJ09}. Our approach is to formulate the
problem as a best-first exploration of an AND/OR tree
(Figure~\ref{fig:andor})~\cite{nilsson1982principles,DBLP:journals/cacm/Hall73}. In
words, the enumeration procedure is best described by the following
recursion: every program is either a primitive combinator OR it is a
left child program applied to a right child program (that is, a left
child AND a right child).

@@

\subsection{Finding the most compressive set of solutions}

@@

\subsection{Re-estimating the stochastic grammar}

@@

\subsection{Boolean function learning}
\label{sec:boolcircuits}

>>>>

\title{Bootstrap Learning via Modular Concept Discovery}

@@

\section{Extracting Concepts from Programs}

@@

\subsection{Representing Typed Functional Programs as Binary Trees}

@@

\subsection{A Stochastic Grammar over Programs}
\label{sec:stochgrammar}

@@

\subsection{Best-first Enumeration of Programs}
In order to explore the frontier of most promising programs, we need a
procedure that enumerates the $N$ most probable expressions. There has
been recent interest in this problem, most of it focused on
enumerating the shortest program satisfying some
criterion~\cite{DBLP:conf/sfp/Katayama05,DBLP:conf/aaip/YakushevJ09}. Our approach is to formulate the
problem as a best-first exploration of an AND/OR tree
(Figure~\ref{fig:andor})~\cite{nilsson1982principles,DBLP:journals/cacm/Hall73}. In
words, the enumeration procedure is best described by the following
recursion: every program is either a primitive combinator OR it is a
left child program applied to a right child program (that is, a left
child AND a right child).

@@

\subsection{Finding the Most Compressive Set of Solutions}

@@

\subsection{Re-estimating the Stochastic Grammar}

@@

\subsection{Boolean Function Learning}
\label{sec:boolcircuits}
